### 2016-07-14 version0.0/intro0.0.tex
Update intro0.0.tex
edits to SFR section

In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using the Bremsstrahlung emission. 
Some of this emission is directly from stars, e.g.\ UV emission, and some is from ISM components that absorb and re-emit light from young stars, e.g.\ far-infrared emission.
Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08} 
Peak of emission of young, hot, and massive stars is in UV wavelength, which makes them an ideal tracer of the current SFR.
One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. 
By knowing the IMF, the number of massive stars can be used to extrapolate the total number of stars formed in a given star-forming region.
To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Sec.~\ref{sec: imf}).
In general each tracer has some systematic errors, and one should decide which tracer is more accurate for a given system.

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
Stellar mass determines the important properties of a star, such as luminosity, lifetime and its evolutionary path. 
One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar initial mass distribution of a star forming region.
Since most SFR calibrations use emission from stars in a specific mass range, it is necessary to know the stellar IMF to extrapolate to the full stellar population.
\cite{Salpeter55} empirically derived the stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
He introduced a power-law IMF $\Phi$  in the form:
\begin{equation}
\label{equ: salp}
\Phi (\log M) = dN / d \log M \propto M^{-\gamma }
\end{equation} 
where $M$ is the stellar mass, $\gamma$ is a power index, and $N$ is the number of stars in the logarithmic mass range of $\log M + d\log M$.

In the late 70s, it was recognised that the assumption of a the single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}. 
Since then, many groups have studied the stellar IMF and found different power-law relations (Fig.~\ref{fig: imf} ). 
Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\cite{Kroupa01}:
\begin{equation}
\begin{split}
    \Phi (\log M) & \propto M^{-2.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
           & \propto M^{-3.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
\end{split}
\end{equation}
Although the Salpeter IMF produces more low-mass stars than the Kroupa IMF, they produce almost the same number of high-mass stars. 
Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF can be converted to the Salpeter IMF by multiplying the calibration constant by 0.67~\citep{Madau14}.
In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars with masses greater than 8~M$_\odot$.
\cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins especially at the high-mass end.

@@

\subsubsection{Resolved Star Formation Indicators}
The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
These objects mostly few million years old and usually are referred to as young stellar objects (YSOs). 
Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$ kpc of the Solar System. 
The number of YSOs can be converted to SFR using: 
\begin{equation}
SFR(YSO) = N_{yso} <M>/\tau 
\end{equation}
where SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$, N$_{yso}$ is the number of YSOs.
$<$M$>$ is the mean mass of YSO which depends on the IMF and considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
$\tau$ is the lifetime of the YSO  $\tau \sim 2$Myr~\citep{Evans09}. 
Since our current devises cannot resolve individual YSOs, this method can only be applied to the Milky Way and its neighbourhood.

In theory, for any system with high enough spatial resolution, counting YSOs can be used as a tracer of the star formation. 
However, considering the limited capabilities of the present instruments, YSOs in most regions beyond the Magellanic Clouds (satellite galaxies of the Milky way with distance of 0.05 Mpc) can not be resolved. 
Therefore, most studies use the emission from the energetic young stars as a tracer of the SFR. 
% Another method to measure the SFR is via colour-magnitude diagrams (CMD) of star-forming regions. 
% \cite{Kennicutt12} discusses the new progress made in the spatially-resolved mapping of CMDs to produce spatially and age-resolved maps of star formation in nearby galaxies. 
% More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to~\citep{Kennicutt12}. %PB: I think you should give a one-sentence summary of the method here. 
%Sr: I think later whether I want to keep this section or not.
\subsubsection{Unresolved Star Formation Indicators}

 In star-forming regions farther away than the Magellanic Clouds, the spatial resolution of currently-available observations is not high enough to find all the young stellar objects. 
 In unresolved systems, calibrating continuum or line emission at wavelengths sensitive to the young massive stars is the primary method of measuring SFR~\citep[e.g.,][]{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}. 
\cite{Kennicutt98b} calibrated the luminosities of galaxies at specific wavelengths for measuring the SFR, using relations between the SFR per unit mass or per unit luminosity and the integrated colour of a system provided by stellar populations synthesis models~\citep[e.g.,][]{Bruzual93}.

In unresolved systems, SFR indicators can be divided into local and global indicators. 
The global SFR indicators are defined for entire galaxies; therefore, they are luminosity-weighted averages across local star formation history and the physical condition inside each galaxy. 
Local calibration is used for regions within a galaxy~\citep[e.g.,][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
Limitations in the spatial resolution of observational data on the one hand, and the broader applicability to distant galaxy populations on the other, have in the past brought more attention to the calibrations of global SFR compared to local SFR. 
Because of its ability to trace the physical processes of the star formation, local SFR calibration is becoming increasingly important~\citep{Calzetti13}.

@@

The most common single-band tracer of star formation rate is the ultraviolet.
As mentioned before, UV emission is an excellent tracer for the SFR.
Using a spectral energy distribution (SED) from Starburst99, with solar metallicity and assuming a~\cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as~\citep{Leitherer99}:
\begin{equation}
SFR(UV) = 3.0 \times 10^{-47}\lambda L_{\lambda}
\end{equation}
where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ could be in the range of $(912< \lambda < 3000~\AA$), and $L_{\lambda}$ is in erg s$^{-1}$\AA.
As shown in Table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
The calibration constants' changes for shorter timescales are more significant and 
the their accuracy is 15 per cent which can vary as a function of $\lambda$~\citep{Calzetti13}.
Ultraviolet light can easily be absorbed or scattered by interstellar dust. 
Therefore, using the UV emission as a tracer might lead to underestimating of the SFR if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section~\ref{sec: ism_intro}).

Another single-band SFR indicator is the emission from hydrogen recombination lines. 
Ionizing photons emitted from young massive stars ionize the surrounding gas. Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ $(0.6563 \mu$m) and H${\beta}$ $(0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}. 
The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived from quantum mechanics. 
The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorbed and re-emited via Ly${\alpha}$ and longer wavelengths.
This is why the H${\alpha}$ emission line strength is greater in optically thick environments. The relation between the SFR, the luminosity of the \halpha emission line and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
\begin{align}
\label{equ: halpha}
SFR(H\alpha) = 5.5 \times 10^{-42}L(H\alpha) \\
                     = 7.4 \times 10^{-54}Q(H^{\circ})
\end{align}
where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions.
Dust extinction (Sec.~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g. by adding L(24$\mu$m) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.

Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727$\AA$. 
Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. 
\cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
Another calibration for this luminosity was derived by \cite{Kennicutt92}. 
In his review on the SFR,~\citep{Kennicutt98b} averaged these calibrations and derived the following relation:
\begin{equation}
SFR([O\ II]) = 1.4 \times 10^{-41} L([O\ II])
\end{equation}  
where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high-redshift galaxies.
In these galaxies, the \halpha emission line is redshifted out of the optical band; as a consequence, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is really useful~\citep{Kennicutt98b}.

Since interstellar dust absorbs approximately half the starlight and re-emits in the infrared, the infrared emission can be used to trace the SFR.
The IR luminosity of a system depends not only on the amount of embedded dust, but also on the heating rate provided by the stars. 
Since young stars heat the dust to higher mean temperatures than old stellar populations, to first order the shape of the thermal IR SED depends on the starlight SED~\citep{Helou86}.
The fact that heating rate provided by the young stellar population is higher than the old stellar population indicates that dust heated by the former is more luminous and consequently its SED peaks at shorter wavelengths (observationally $\approx 60~\mu$m) in comparison with dust heated by old or low-mass stars.
Therefore, infrared observations are able to detect the emission from the dust heated by young stellar populations, and can be used as an SFR indicator.

@@

The emission from dust heated by young stars changes by amount of high energy photon emitted to dust and by properties of dust such as grain size.
Therefore, calibration of SFR varies with each single-band IR emission.
Assuming that dust heating is dominated by emission from young stars stellar, integrating over the full wavelength range of the infrared part of the spectrum gives the total infrared (TIR) emission of a system, which can be used as an SFR indicator~\citep{Kennicutt98b}.

TIR luminosity can be measured from the integrated infrared SED or a calibration of spatially-resolved infrared photometry introduced by~\cite{Draine07}. 
\cite{Boquien10} modified calibration of the total infrared luminosity as: 
\begin{equation}
L(\rm TIR) = 0.95L(PAH 8 \mu m) + 1.15L(24 \mu m) + L(70 \mu m) + L(160 \mu m)
\end{equation}
where $L = \nu L_{\nu}$ is the luminosity in erg~s$^{-1}$ at frequency $\nu$. 
\cite{Calzetti07} indicated that the star formation rate calibration for a stellar population undergoing constant star formation over $\tau=$100~Myr is:
\begin{equation}
\label{sfr_tot_IR}
SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR)
\end{equation}
where SFR(TIR) is in M${\odot}$~yr$^{-1}$, and L(TIR) is in erg~s$^{-1}$.

In Sec~\ref{sec: overview} we mentioned that emission from PAHs in ISM can be used as SFR indicator~\citep[e.g.][]{Peeters04}.
Most studies used broad bands IR emission, which contain PAHs, to calibrate SFR~\citep[e.g.][]{Calzetti07}, but SFR can be calibrated using the PAH features only.
\cite{Shipley16} calibrated SFR using observation from 105 star-forming galaxies with $z < 0.4$ as:
\begin{equation}
\log SFR = A + B \log L_{\mathrm{PAH}, \lambda}
\end{equation}
where $L_{\mathrm{PAH}, \lambda}$ is the luminosity of the PAH features at 6.2, 7.7, 11.3~$\mu$m or combinations thereof, in erg~s$^{-1}$.
Tab.~\ref{table_PAH} shows the constants for each $L_{\mathrm{PAH}, \lambda}$.
These calibrations underestimate the SFR for low-redshift galaxies with IR luminosity more than $10^12$~erg~s$^{-1}$.
\cite{Shipley16} showed that using the 7.7~$\mu$m feature in the calibration reduces the scatter and concluded that this wavelength provides the most robust SFR tracer.

@@

The most common use of combining luminosities to trace the SFR is the combination of total infrared measurements with both far- and near-ultraviolet observations, with the latter being more commonly used. 
This combination helps to avoid uncertainties from corrections for dust attenuation in far-UV (FUV) observations~\citep[e.g.][]{Hao11}. The calibration is:
\begin{equation}
L_{FUV}(\rm corr) = L_{FUV}(\rm obs) + \alpha L_{\rm TIR}
\end{equation}
where the luminosities are $L = \nu L_{\nu}$ in erg~s$^{-1}$, and the coefficient $\alpha$ depends on the bandpasses chosen for the UV and IR measurements. $\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies are from dust heated by older populations of stars~\citep{Kennicutt12}. The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs (~\citep[e.p][]{Hao11, Leroy08}.

Another common method for using the multi-wavelength indicator for star formation is using H${\alpha}$ emission in combination with the 24~$\mu$m emission. 
This combination gives a more accurate dust-corrected estimate of the SFR~\citep{Kennicutt09}:
\begin{equation} 
\label{equ: halphaplus24}
SFR = 7.9 \times 10^{-42}[L(H{\alpha})_{\rm obs} + 0.020L(24)]
\end{equation}
where L(H${\alpha}$)$_{\rm obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$. 
L(24) is the 24~$\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}$~yr$^{-1}$.

The IR emission in the other band can be used for correcting dust effect on UV or \halpha~emission (see Tab.~\ref{table3}). 
The corrected emission then can be used as a SFR tracer.
These composite SFR indicators also have systematic uncertainties; yet, it seems that there is good correlation between multi-band tracers and single-band tracers. 
Moreover, less uncertainty arises in this case than when using the single-band emission as a tracer~\citep{Kennicutt09}.

@@

%PB: would it make sense to put this paragraph closer to where you first discuss Table 1? Sahar: I thought because IMF affect all of the calibration it would be better to have at the end of the section.
As mentioned in Section~\ref{sec: imf}, using different IMFs results in having different calibration constants for star formation rate. 
From Table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. 
This effect is more than four times larger than for UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV wavelengths than the other part of spectrum; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$.
Furthermore, reaching an asymptotic value of ionizing photons takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). 
Therefore, changes in the H${\alpha}$ SFR calibration constant are more pronounced, while for UV and TIR the calibration constants are fairly close to each other.
On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than a 10 per cent difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$. 
As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars~\citep{Calzetti13}.

>>>>

In principle, emission from new stars can be traced by ultraviolet, visible light, near-IR and radio wavelengths, hydrogen recombination lines, forbidden metal lines, and also in the sub-mm range by using  Bremsstrahlung emission. 
Some of this emission is directly from stars, e.g.\ UV emission, and some is from ISM components that absorb and re-emit light from young stars, e.g.\ far-infrared emission.
Techniques to calibrate emission from newly-born stars, preferably hot and massive ones, to the rate at which stars are being formed have been the subject of many studies~\citep[e.g.][]{Calzetti07, Kennicutt11, Hao11,Bigiel08} 
The peak of emission of young, hot, and massive stars is at UV wavelengths, which makes them an ideal tracer of the current SFR.
One of the main assumptions in using the luminosity of massive stars is that the SFR has remained largely constant during the timescale probed by the specific wavelength which is being used as the tracer. 
By knowing the IMF, the number of massive stars can be used to extrapolate to the total number of stars formed in a given star-forming region.
To have a reliable SFR indicator, the stellar IMF must be fully sampled to have at least one star in all mass bins (for more detail see Sec.~\ref{sec: imf}).
In general each tracer has some systematic errors, and one should decide which tracer is more accurate for a given system.

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
Stellar mass determines the important properties of a star, such as luminosity, lifetime and its evolutionary path. 
One of the most fundamental and difficult questions that a complete theory of star formation must answer is ``what is the stellar initial mass distribution?'' of a star forming region.
Since most SFR calibrations use emission from stars in a specific mass range, it is necessary to know the stellar IMF to extrapolate to the full stellar population.
\cite{Salpeter55} empirically derived the stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
He introduced a power-law IMF $\Phi$  in the form:
\begin{equation}
\label{equ: salp}
\Phi (\log M) = dN / d \log M \propto M^{-\gamma }
\end{equation} 
where $M$ is the stellar mass, $\gamma$ is a power index, and $N$ is the number of stars in the logarithmic mass range of $\log M + d\log M$.

In the late 70s, it was recognised that the assumption of a single power-law IMF over all stellar masses is not correct and might overestimate the number of low-mass stars~\citep{Kroupa93, Bastin10}. 
Since then, many groups have studied the stellar IMF and found different power-law relations (Fig.~\ref{fig: imf} ). 
Most SFR calibrations have the same assumption that the stellar IMF is constant across all environments and adopt it from the standard stellar IMF introduced by\cite{Kroupa01}:
\begin{equation}
\begin{split}
    \Phi (\log M) & \propto M^{-2.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
           & \propto M^{-3.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
\end{split}
\end{equation}
Although the Salpeter IMF produces more low-mass stars than the Kroupa IMF, they produce almost the same number of high-mass stars. 
Therefore, the SFR calibrations, which mostly trace massive stars in galaxies, can be converted from the Kroupa IMF  to the Salpeter IMF by multiplying the calibration constant by 0.67~\citep{Madau14}.
In a more recent study,~\cite{Weisz15} used data from the Panchromatic Hubble Andromeda Treasury program~\citep[PHAT][]{Dalcanton12} and showed that for nearby galaxies both Kroupa and Salpeter stellar IMFs overestimate the number of stars with masses greater than 8~M$_\odot$.
\cite{Bastin10} reviewed the stellar IMF as derived from many observational results and showed that the stellar IMF is constant and universal, though there are uncertainties in different mass bins, especially at the high-mass end.

@@

\subsubsection{Resolved Star Formation Indicators}
The most direct way to measure the SFR and trace recent star formation is counting individual objects~\citep{Kennicutt12}. 
These objects are mostly a few million years old and  are usually referred to as young stellar objects (YSOs). 
Counting YSOs is used for calculating star formation rates in molecular clouds within $0.5- 1$ kpc of the Solar System. 
The number of YSOs can be converted to SFR using: 
\begin{equation}
SFR(YSO) = N_{yso} <M>/\tau 
\end{equation}
where SFR(YSO) is in units of M$_{\odot}$~yr$^{-1}$, N$_{yso}$ is the number of YSOs.
$<$M$>$ is the mean mass of YSO which depends on the IMF; considering current IMFs $<$M$> = $0.5~M$_{\odot}$ ~\citep[][]{Kennicutt12}. 
$\tau$ is the lifetime of the YSO  $\tau \sim 2$Myr~\citep{Evans09}. 
Since our current devices cannot resolve individual YSOs in distant galaxies, this method can only be applied to the Milky Way and its neighbourhood.

In theory, for any system with high enough spatial resolution, counting YSOs can be used as a tracer of the star formation. 
However, considering the limited capabilities of present instruments, YSOs in most regions beyond the Magellanic Clouds (satellite galaxies of the Milky Way with a distance of 0.05 Mpc) cannot be resolved. 
Therefore, most studies use the emission from energetic young stars as a tracer of the SFR. 
% Another method to measure the SFR is via colour-magnitude diagrams (CMD) of star-forming regions. 
% \cite{Kennicutt12} discusses the new progress made in the spatially-resolved mapping of CMDs to produce spatially and age-resolved maps of star formation in nearby galaxies. 
% More detailed studies of CMDs are not in the scope of this paper; for more information, one can refer to~\citep{Kennicutt12}. %PB: I think you should give a one-sentence summary of the method here. 
%Sr: I think later whether I want to keep this section or not.
\subsubsection{Unresolved Star Formation Indicators}

 In star-forming regions farther away than the Magellanic Clouds, the spatial resolution of currently-available observations is not high enough to find all the young stellar objects. 
 In unresolved systems, calibrating continuum or line emission at wavelengths sensitive to young massive stars is the primary method of measuring SFR~\citep[e.g.,][]{Kennicutt98b, Kewley02, Bell03, Calzetti07, Calzetti08, Calzetti10, Calzetti13, Kennicutt07, Kennicutt09, Boquien10, Hao11, Kennicutt12}. 
\cite{Kennicutt98b} calibrated the luminosities of galaxies at specific wavelengths for measuring the SFR, using relations between the SFR per unit mass or per unit luminosity and the integrated colour of a system provided by stellar population synthesis models~\citep[e.g.,][]{Bruzual93}.

In unresolved systems, SFR indicators can be divided into local and global indicators. 
The global SFR indicators are defined for entire galaxies; therefore, they are luminosity-weighted averages across local star formation history and the physical condition inside each galaxy. 
Local calibrations are used for regions within a galaxy~\citep[e.g.,][]{Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
Limitations in the spatial resolution of observational data on the one hand, and the broader applicability to distant galaxy populations on the other, have in the past brought more attention to the calibrations of global SFR compared to local SFR. 
Because of its ability to trace the physical processes of the star formation, local SFR calibration is becoming increasingly important~\citep{Calzetti13}.

@@

The most common single-band tracer of star formation rate is the ultraviolet.
As mentioned before, UV emission is an excellent tracer for the SFR.
Using a spectral energy distribution (SED) from Starburst99, with solar metallicity and assuming a~\cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as~\citep{Leitherer99}:
\begin{equation}
SFR(UV) = 3.0 \times 10^{-47}\lambda L_{\lambda}
\end{equation}
where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ could be in the range of $(912< \lambda < 3000~\AA$), and $L_{\lambda}$ is in erg s$^{-1}$\AA. %PB: should be \AA$^{-1}$? please check.
As shown in Table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
The calibration constants' changes for shorter timescales are more significant and 
their accuracy is 15 per cent which can vary as a function of $\lambda$~\citep{Calzetti13}.
Ultraviolet light can easily be absorbed or scattered by interstellar dust. 
Therefore, using the UV emission as a tracer might lead to underestimation of the SFR if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section~\ref{sec: ism_intro}).

Another single-band SFR indicator is the emission from hydrogen recombination lines. 
Ionizing photons emitted from young massive stars ionize the surrounding gas. Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ $(0.6563 \mu$m) and H${\beta}$ $(0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}. 
The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived from quantum mechanics. 
The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorbed and re-emitted via Ly${\alpha}$ and longer wavelengths.
This is why the H${\alpha}$ emission line strength is greater in optically thick environments. The relation between the SFR, the luminosity of the \halpha emission line and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
\begin{align}
\label{equ: halpha}
SFR(H\alpha) = 5.5 \times 10^{-42}L(H\alpha) \\
                     = 7.4 \times 10^{-54}Q(H^{\circ})
\end{align}
where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in \hii~regions.
Dust extinction (Sec.~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g. by adding L(24$\mu$m) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.

Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727$\AA$. 
Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
As a result, \oii~luminosity can be used as a tracer of the SFR through the \halpha luminosity. 
\cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
Another calibration for this luminosity was derived by \cite{Kennicutt92}. 
In his review on the SFR,~\citep{Kennicutt98b} averaged these calibrations and derived the following relation:
\begin{equation}
SFR([O\ II]) = 1.4 \times 10^{-41} L([O\ II])
\end{equation}  
where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of the major SFR indicators in high-redshift galaxies.
In these galaxies, the \halpha emission line is redshifted out of the optical band; as a consequence, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is really useful~\citep{Kennicutt98b}.

Since interstellar dust absorbs approximately half the starlight and re-emits in the infrared, the infrared emission can be used to trace the SFR.
The IR luminosity of a system depends not only on the amount of embedded dust, but also on the heating rate provided by the stars. 
Since young stars heat the dust to higher mean temperatures than old stellar populations, to first order the shape of the thermal IR SED depends on the starlight SED~\citep{Helou86}.
The fact that the heating rate provided by the young stellar population is higher than  that of the old stellar population indicates that dust heated by the former is more luminous and consequently its SED peaks at shorter wavelengths (observationally $\approx 60~\mu$m) in comparison with dust heated by old or low-mass stars.
Therefore, infrared observations are able to detect the emission from the dust heated by young stellar populations, and can be used as an SFR indicator.

@@

The emission from dust heated by young stars changes with the amount of high energy photons heating the dust and by properties of dust such as grain size.
Therefore, the calibration of SFR varies with each infrared band.
Assuming that dust heating is dominated by emission from young stars, integrating over the full wavelength range of the infrared part of the spectrum gives the total infrared (TIR) emission of a system, which can be used as an SFR indicator~\citep{Kennicutt98b}.

TIR luminosity can be measured from the integrated infrared SED or a calibration of spatially-resolved infrared photometry introduced by~\cite{Draine07}. 
\cite{Boquien10} modified the calibration of the total infrared luminosity as: 
\begin{equation}
L(\rm TIR) = 0.95L(PAH 8 \mu m) + 1.15L(24 \mu m) + L(70 \mu m) + L(160 \mu m)
\end{equation}
where $L = \nu L_{\nu}$ is the luminosity in erg~s$^{-1}$ at frequency $\nu$. 
\cite{Calzetti07} indicated that the star formation rate calibration for a stellar population undergoing constant star formation over $\tau=$100~Myr is:
\begin{equation}
\label{sfr_tot_IR}
SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR)
\end{equation}
where SFR(TIR) is in M${\odot}$~yr$^{-1}$, and L(TIR) is in erg~s$^{-1}$.

In Sec.~\ref{sec: overview} we mentioned that emission from PAHs in the ISM can be used as SFR indicator~\citep[e.g.][]{Peeters04}.
Most studies used broad infared bands, which contain PAHs, to calibrate SFR~\citep[e.g.][]{Calzetti07}, but SFR can be calibrated using the PAH features only.
\cite{Shipley16} calibrated SFR using observation from 105 star-forming galaxies with $z < 0.4$ as:
\begin{equation}
\log SFR = A + B \log L_{\mathrm{PAH}, \lambda}
\end{equation}
where $L_{\mathrm{PAH}, \lambda}$ is the luminosity of the PAH features at 6.2, 7.7, 11.3~$\mu$m or combinations thereof, in erg~s$^{-1}$.
Tab.~\ref{table_PAH} shows the constants for each $L_{\mathrm{PAH}, \lambda}$.
These calibrations underestimate the SFR for low-redshift galaxies with IR luminosity more than $10^12$~erg~s$^{-1}$.
\cite{Shipley16} showed that using the 7.7~$\mu$m feature in the calibration reduces the scatter and concluded that this wavelength provides the most robust SFR tracer.

@@

The most common use of combining luminosities to trace the SFR is the combination of total infrared measurements with both far- and near-ultraviolet observations, with the latter being more commonly used. 
This combination helps to avoid uncertainties from corrections for dust attenuation in far-UV (FUV) observations~\citep[e.g.][]{Hao11}. The calibration is:
\begin{equation}
L_{FUV}(\rm corr) = L_{FUV}(\rm obs) + \alpha L_{\rm TIR}
\end{equation}
where the luminosities are $L = \nu L_{\nu}$ in erg~s$^{-1}$, and the coefficient $\alpha$ depends on the bandpasses chosen for the UV and IR measurements. $\alpha$ is usually less than 1 because significant amounts of IR emission in many galaxies are from dust heated by older populations of stars~\citep{Kennicutt12}. The coefficient $\alpha$ is calibrated both theoretically, using evolutionary synthesis models, and empirically, by using measurements of dust corrected SFRs (~\citep[e.g.][]{Hao11, Leroy08}.

Another common multi-wavelength indicator for star formation is using H${\alpha}$ emission in combination with the 24~$\mu$m emission. 
This combination gives a more accurate dust-corrected estimate of the SFR~\citep{Kennicutt09}:
\begin{equation} 
\label{equ: halphaplus24}
SFR = 7.9 \times 10^{-42}[L(H{\alpha})_{\rm obs} + 0.020L(24)]
\end{equation}
where L(H${\alpha}$)$_{\rm obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the units of erg~s$^{-1}$. 
L(24) is the 24~$\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}$~yr$^{-1}$.

Infrared emission in other bands can be used for correcting dust effects on UV or \halpha~emission (see Tab.~\ref{table3}). 
The corrected emission then can be used as a SFR tracer.
These composite SFR indicators also have systematic uncertainties; yet, it seems that there is good correlation between multi-band tracers and single-band tracers. 
Moreover, less uncertainty arises in this case than when using the single-band emission as a tracer~\citep{Kennicutt09}.

@@

%PB: would it make sense to put this paragraph closer to where you first discuss Table 1? Sahar: I thought because IMF affect all of the calibration it would be better to have at the end of the section. %PB: OK.
As mentioned in Section~\ref{sec: imf}, using different IMFs results in having different calibration constants for star formation rate. 
From Table~\ref{table1} it is clear that changing the IMF affects the H${\alpha}$ SFR calibration more than other SFR calibrations. 
This effect is more than four times larger than for UV SFR calibrations because newly-formed stars having up to $\sim 5$ M$_{\odot}$ emit more strongly at UV wavelengths than in other parts of the spectrum; however, significant amounts of ionising photons are produced by stars more massive than $\sim 20$ M$_{\odot}$.
Furthermore, reaching an asymptotic value of ionizing photons takes longer for more massive stars (10 Myr for the upper mass limit of 30 M$_{\odot}$ versus 6 Myr for 100 M$_{\odot}$). 
Therefore, changes in the H${\alpha}$ SFR calibration constant are more pronounced, while for UV and TIR the calibration constants are fairly close to each other.
On the other hand, using the mean stellar mass for the Kroupa IMF $(<$M$> \sim 0.6$ M$_{\odot})$ yields less than a 10 per cent difference between using the upper mass limit of 100 M$_{\odot}$ and 30 M$_{\odot}$. 
As a result, calibrations derived with the mean stellar mass of a system are more accurate than those that are based on tracing the most massive stars~\citep{Calzetti13}.
